### 2022-06-25 manuscript/manuscript.Rmd
Improve redaction of statistical methods for GAMs

Generalized additive models (GAM) were used to describe linear and non-linear relationships in the form of smooth terms between developmental characteristics, represented through penalized regression splines [@wood2011fast]. Restricted maximum likelihood method was used for the estimation of the smoothing parameters, and thin-plate regression splines for smoothing basis, as they are the optimal smoother of any given basis dimension/rank [@wood2003thin]. To describe the smooth terms by means of quasi-linear segments, we used approximative effect derivatives with 95% confidence intervals.

>>>>

Generalized additive models (GAM) were used to describe linear and non-linear relationships in the form of smooth terms between developmental characteristics, represented through penalized regression splines [@wood2011fast]. Restricted maximum likelihood method was used for the estimation of the smoothing parameters, and thin-plate regression splines as the smoothing basis, as they are the optimal smoother of any given basis dimension/rank [@wood2003thin]. To describe the smooth terms by means of quasi-linear segments, we used approximative effect derivatives with 95% confidence intervals (CI~95%~).
